Probabilistic Programming

### 2014-04-20 paper/paper.tex
Update paper.tex
Finished Introduction (early draft)

\section{Introduction}
For many people just starting out, programming can seem like a confusing and tedious activity. It can be unclear for 
many new programmers where they should begin and what should come next while coding. Without any proper guidance, 
a novice programmer is left on their own to scour thousands of pages online to discover what should come next in 
their code. Then, once a person becomes more adept at programming, he or she may notice that they are typing out 
the same or similar lines of code within each new program. This repetitiveness slows down the user and can make 
programming a much more tiresome task than it needs to be. 
\subsection{Motivation}

>>>>

\section{Introduction}
For many people just starting out, programming can seem like a confusing and tedious activity. It can be unclear for 
many new programmers where they should begin and what should come next while coding. Without any proper guidance, 
a novice programmer is left on their own to scour thousands of pages online to discover what should come next in 
their code. Then, once a person becomes more adept at programming, he or she may notice that they are typing out 
the same or similar lines of code within each new program. This repetitiveness slows down the user and can make 
programming a much more tiresome task than it needs to be. These observations steered our group towards developing
a way for someone to code with guidance. The Probabilistic Programming method allows for a user to code in JavaScript
using a web application. This web app provides a list of suggestions for the user's next line of code depending on where
the user is in the program. Not only is this helpful for new programmers that need suggestions for what to write next 
in their code, this system allows for expert programmers to write code with a great deal more ease and efficiency.
\subsection{Motivation}
